\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.75in,top=0.4in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\name{Chetan Modhavadiya}  % Your name
\address{ +91-9974806891 \\ modhvadiyac25@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education} 

{\bf Bachelor of Technology} \hfill {\em 2019-2022} \\ 
Dharmsinh Desai University - Nadiad \smallskip \\
Overall CPI:  10/7.2

{\bf Diploma In Computer Engineering} \hfill {\em 2016-2019} \\ 
Atmiya Institute of Technology and Science for Diploma Studies - Rajkot \smallskip \\
Overall CGPA: 10/8.9

{\bf Royal Science School - Dhoraji} \hfill {\em 2015-2016} \\ 
\textbf{10th} Percentage :- 82.16 \% 

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Major Projects}

\begin{rSubsection}{Find My Car}{}{}{}
\item Find my car is developed in \textbf{Android} with \textbf{Kotlin} and \textbf{Firebase} as backend and \textbf{Xml} as frontend. where users can watch various car specifications, top 10 cars, most popular cars, and many other details about cars apart from that it keeps its user up to date with automobile news.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{QuizeHub}{}{}{}
\item QuizeHub is developed in \textbf{\texttt{C\#}}, \textbf{DOTNET Core with Entity Framework Core}, and \textbf{Microsoft SqlServer}.it is a web-based platform where users can play quizzes by answering questions asked into the quiz. Admin can upload quiz questions based on the various categories. 
\end{rSubsection}

%------------------------------------------------
\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Other Projects}

\begin{rSubsection}{Online Notice Board}{}{}{}
\item ONB is implemented in \textbf{java (servlet, JSP)}, \textbf{HTML}, \textbf{CSS}, \textbf{JavaScript}, and \textbf{MySQL}. Where faculty members can upload the circulars and students can view the uploaded documents.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Budget Management System}{}{}{}
\item BMS is a Web-API-based project developed in DotNet Technology with \texttt{C\#} and Microsoft SqlServer.in this project, Web-API provides the employee’s whole income and expense details. apart from that employees can add their income and expense along with various categories. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Find My Work}{}{}{}
\item FMW is a web application developed with \textbf{MEAN Stack}.it provides information about work to do. Users can choose work as per their convenience. 
\end{rSubsection}


%------------------------------------------------
\end{rSection}





%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Languages  and Technologies}
\begin{itemize}
\item \textbf{Languages :} C, C++, Java, Php, python, Ajax, Jquery.
\item \textbf{Frameworks and tools :} Android Studio,Spring(Basic), DOTNET Core,Web-Service,Web-Api.
\item \textbf{Other : }Git, Github(intermediate), AWS-Developer tools (Basic)
\end{itemize}
\end{rSection}


%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Linkes}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
LinkedIn &  \url{www.linkedin.com/in/chetan-modhavadiya-a168a3138} \\
GitHub & \url{https://github.com/modhvadiyac25}\\
HackerRank & \url{https://www.hackerrank.com/modhvadiyac25/}\\
\end{tabular}

\end{rSection}

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
